A weakly structured stem for human origins in Africa

### 2022-03-01 paper.tex
Figure 3 captions

\begin{figure}[t!]
    \centering
    \includegraphics{figures/fig3.pdf}
    \caption{
        \textbf{Predicted population structure over time.}
        From the best fit models of our two parameterizations (top row:
        continuous migration, bottom row: merger with stem migration), we computed
        predicted differentiation between contemporaneous populations over time
        as $H_{i,j}$, the expected pairwise diversity between two samples, one
        each from populations $i$ and $j$.
        We also computed the proportion of drift between pairs of sampled
        populations that aligns with drift between populations in the past
        ($\alpha^2$, see Section~\ref{sec:f4} in the Supplement).
        While both models inferred population structure to extend deep into the
        past, the ancient structure contributes relatively little to present-day
        differentiation between human populations.
    }
    \label{fig:3}
\end{figure}

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics{figures/fig3.pdf}
    \caption{
        \textbf{Predicted population structure over time.}
        From the best fit models of our two parameterizations (top row:
        continuous migration, bottom row: merger with stem migration), we predicted
       pairwise differences $H_{i,j}$ between individuals sampled from populations $i$ and $j$ 
       existing at time $t$. 
        To understand how drift between stems explains present-day structure, 
        we also computed the proportion $\alpha^2$ of drift between pairs of sampled present-day
        populations that aligns with drift between past populations (Here Nama and Mende, see Section~S\ref{sec:f4} for details and additional comparisons \sgcomment{do we have extra comparisons there?}).
        Both models infer deep population structure with modest contributions to present-day genetic differentiation. Most present differentiation dates back to the last 100kya.}
    \label{fig:3}
\end{figure}
